Real-Time Image Recognition Using Collaborative IoT Devices

### 2018-06-13 dissemination.publication/640fb4c4b9ba9822/paper.tex
added ISBN
minor clean up

% ISBN
% \acmISBN{123-4567-24-567/08/06}

@@

\begin{verbatim}
$ ck run program:request-iot-benchmark --cmd_key=benchmark-alexnet-farm-5-nodes-start-server --target=farm-5 
\end{verbatim}
Now you can run benchmark for distributed inference as follows:
\begin{verbatim}
$ ck run program:request-iot-benchmark --cmd_key=benchmark-alexnet-farm-5-nodes --target=farm-5
   --env.STAT_REPEAT=5
\end{verbatim}

@@

Now start server on all nodes as follows:
\begin{verbatim}
$ ck run program:request-iot-benchmark --cmd_key=benchmark-vgg16-farm-9-nodes-start-server --target=farm-9 
\end{verbatim}
Now you can run benchmark for distributed inference as follows:
\begin{verbatim}
$ ck run program:request-iot-benchmark --cmd_key=benchmark-vgg16-farm-9-nodes --target=farm-9
    --env.STAT_REPEAT=5
\end{verbatim}

@@

For VGG16 with 11 nodes, create ''farm-11.json'' and register farm-11 machine:
\begin{verbatim}
{
    "node":
    {
        "initial": [
            "192.168.1.8"
        ],
        "block12345": [
            "192.168.1.3","192.168.1.4","192.168.1.5","192.168.1.6","192.168.1.7","192.168.1.9","192.168.1.10"
        ],
        "fc1": [
            "192.168.1.11", "192.168.1.13"
        ],
        "fc2": [
            "192.168.1.12"
        ]
    }
}
\end{verbatim}

@@

Now start server on all nodes as follows:
\begin{verbatim}
$ ck run program:request-iot-benchmark --cmd_key=benchmark-vgg16-farm-11-nodes-start-server --target=farm-11 
\end{verbatim}
Now you can run benchmark for distributed inference as follows:
\begin{verbatim}
$ ck run program:request-iot-benchmark --cmd_key=benchmark-vgg16-farm-11-nodes --target=farm-11
   --env.STAT_REPEAT=5
\end{verbatim}

>>>>

% ISBN
\acmISBN{978-1-4503-5923-8}

@@

\begin{verbatim}
$ ck run program:request-iot-benchmark --cmd_key=benchmark-alexnet-farm-5-nodes-start-server \
    --target=farm-5 
\end{verbatim}
Now you can run benchmark for distributed inference as follows:
\begin{verbatim}
$ ck run program:request-iot-benchmark --cmd_key=benchmark-alexnet-farm-5-nodes --target=farm-5 \
   --env.STAT_REPEAT=5
\end{verbatim}

@@

Now start server on all nodes as follows:
\begin{verbatim}
$ ck run program:request-iot-benchmark --cmd_key=benchmark-vgg16-farm-9-nodes-start-server \
     --target=farm-9 
\end{verbatim}
Now you can run benchmark for distributed inference as follows:
\begin{verbatim}
$ ck run program:request-iot-benchmark --cmd_key=benchmark-vgg16-farm-9-nodes --target=farm-9 \
    --env.STAT_REPEAT=5
\end{verbatim}

@@

For VGG16 with 11 nodes, create ''farm-11.json'' and register farm-11 machine:
\begin{verbatim}
{
    "node":
    {
        "initial": [
            "192.168.1.8"
        ],
        "block12345": [
            "192.168.1.3","192.168.1.4","192.168.1.5","192.168.1.6",
            "192.168.1.7","192.168.1.9","192.168.1.10"
        ],
        "fc1": [
            "192.168.1.11", "192.168.1.13"
        ],
        "fc2": [
            "192.168.1.12"
        ]
    }
}
\end{verbatim}

@@

Now start server on all nodes as follows:
\begin{verbatim}
$ ck run program:request-iot-benchmark --cmd_key=benchmark-vgg16-farm-11-nodes-start-server \
    --target=farm-11 
\end{verbatim}
Now you can run benchmark for distributed inference as follows:
\begin{verbatim}
$ ck run program:request-iot-benchmark --cmd_key=benchmark-vgg16-farm-11-nodes --target=farm-11 \
    --env.STAT_REPEAT=5
\end{verbatim}
